\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-03-17 paper.tex
First pass on theory of mind

Second remark, after some research (see appendix B of~\cite{ma these} for a
detailled discussion)  we have decided not to represent neither tasks nor plans
in the ontology: the planning domain (with tasks pre- and postconditions) is
stored in a specific format, outside of the knowledge repository, and the
resulting plans are directly communicated to the robot controller. The ontology
formalism that we have adopted (namely OWL) does not appear to be a satisfaying
reprepresentation language for concepts that are both tightly bound to time
representation and non-monotonic. Other researches (\cite{tenorth...}) have attempted with more success (\fixme{regarder ca!!}).

@@

\cite{Warnier2012a}

>>>>

Second remark, after some research (see appendix B of~\cite{Lemaignan2012a} for a
detailled discussion)  we have decided not to represent neither tasks nor plans
in the ontology: the planning domain (with tasks pre- and postconditions) is
stored in a specific format, outside of the knowledge repository, and the
resulting plans are directly communicated to the robot controller. The ontology
formalism that we have adopted (namely OWL) does not appear to be a satisfaying
reprepresentation language for concepts that are both tightly bound to time
representation and non-monotonic. Other researches (\cite{tenorth...}) have attempted with more success (\fixme{regarder ca!!}).

@@

Theory of Mind (originally defined in~\cite{Premack1978}) is the
cognitive ability that a subject has to represent the mental state of another
agent, possibly including knowledge that contradicts the subject own model: for
example, a book can be at the same time visible by myself, and not visible by
you.

This skill, which is essential to understand others' perspectives during
interactions, appears in children around their third year. It supposes the ability to build, store and retrieve separate models of the knowledge of the interactors.

Our knowledge base implements such a mechanism: when the robots infers a new
agent has been introduced in the knowledge base, it initializes a new,
independant, ontology for this agent. All the ontologies that are created share
the same common-sense knowledge, but rely on each agent's perspective for the
actual instantiation: the robot (geometrically) computes that the book is in
its own field of view, but not in the human one. The robot knowledge contains
the fact \stmt{book isVisible true} while the human model contains \stmt{book
isVisible false}.

The \cite{Warnier2012a}
